\documentclass[11pt, preprint]{aastex}
\usepackage{graphicx}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage{natbib}
\usepackage{epsfig}
\setlength{\parindent}{0in}
\newcommand{\ha}{$H\alpha$}
\newcommand{\rtwo}{$R_{200}$}
\newcommand{\size}{$ R_e(24)/R_e(r)$}
\newcommand{\sizeb}{$ R_e(22)/R_e(r)$}
% \newcommand{\dr}{$\Delta R/R_{200}$}
\newcommand{\lcs}{$Local \ Cluster \ Survey $}
\newcommand{\rad}{$R_e$}
\newcommand{\sers}{{\it S\'{e}rsic}}
%\newcommand{\micron}{{$\mu m$}}
%\newcommand{\arcsec}{$"$}

%\pagestyle{myheadings}
%\markright{RUI: Collaborative Research: The Effect of Filaments on the
%  Gas in Galaxies \hfill Finn \& Rudnick~~}


\begin{document}

\noindent\textbf{\Large CURRENT AND PENDING SUPPORT}\\
Investigator: Gregory Rudnick, University of Kansas \\
Other agencies to which this proposal has been/will be submitted: None \\


\textbf{Pending Support}
\\
Project/Proposal Title: This Proposal - Collaborative Research: The Effect of Filaments on the Gas in Galaxies\\
Source of support: NSF\
Total Award Amount: \textbf{\$382,878}\\
Total Award Period Covered: 1/1/2018-12/31/2020\\
Location of Project: The University of Kansas, Lawrence, KS \\
Person-Months Per Year Committed to the Project: Year 1-3, Su. 1.0\\

\textbf{Current Support}
\\
Project/Proposal Title: “ Confronting models of star formation quenching in galaxy clusters with archival Spitzer data\\
Source of support: NASA ROSES ADAP\\
Total Award Amount: \textbf{\$159,520}\\
Total Award Period Covered: 1/1/2017-12/31/2018\\
Location of Project: The University of Kansas, Lawrence, KS \\
Person-Months Per Year Committed to the Project: Year 1, Su. 1.0 : Year 2, Su. 0.03\\

Project/Proposal Title: The role of quenching and merging in shaping the passive galaxy population in distant clusters\\
Source of support: Space Telescope Science Institute, Cycle 23\\
Total Award Amount: \textbf{\$149,855}\\
Total Award Period Covered: 1/1/2016-12/31/2017\\
Location of Project: The University of Kansas, Lawrence, KS \\
Person-Months Per Year Committed to the Project: Year 1, Su. 1.0 : Year 2, Su. 0.5\\
\\
Project/Proposal Title: The GOGREEN Survey: Caring about the Environment\\
Source of support: NSF\\
Total Award Amount: \textbf{\$347,556} \\
Total Award Period Covered: 8/1/2015-7/31/2018\\
Location of Project: The University of Kansas, Lawrence, KS \\
Person-Months Per Year Committed to the Project: Year 1-3, Su. 1.0 \\
\\
Project/Proposal Title: Galaxy Transformation in the Infall Regions of Clusters \\
Source of support: Space Telescope Science Institute, Cycle 21\\
Total Award Amount: \textbf{\$17,239}\\
Total Award Period Covered: 4/1/2014-3/31/2017 \\
Location of Project: The University of Kansas, Lawrence, KS \\
Person-Months Per Year Committed to the Project: Year 1, Su. 1.0\\
\\
Project/Proposal Title: Spatially Resolved Observations of Gas Stripping in Intermediate Redshift Clusters and Groups\\
Source of support: Space Telescope Science Institute, Cycle 20\\
Total Award Amount: \textbf{\$119,978} \\
Total Award Period Covered: 12/1/2012 - 11/30/2016\\
Location of Project: The University of Kansas, Lawrence, KS \\
Person-Months Per Year Committed to the Project: Year 1-3, Su. 1.\\
%\\
%Project/Proposal Title: Characterizing the Molecular Gas Contents of High Redshift Galaxies\\
%Source of support: NSF\\
%Total Award Amount: \textbf{\$318,286} \\
%Total Award Period Covered: 8/1/2012-7/31/2016\\
%Location of Project: The University of Kansas, Lawrence, Kansas\\
%Person-Months Per Year Committed to the Project: Year 1-2, Su. 0.0; Year 3, Su. 2.0\\

\end{document}
