\documentclass[11pt, preprint]{aastex}
\usepackage{graphicx}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage{natbib}
\usepackage{epsfig}
% \usepackage{epsfig, xcolor, footnote, mdwlist, wrapfig}
% \usepackage{hyperref}
% \usepackage[flushleft]{threeparttable}
% \usepackage{sidecap}
% \usepackage{simplemargins}
% \usepackage[compact]{titlesec}
% \usepackage{times}
% \usepackage{amsmath}
% \usepackage[]{natbib}
% \usepackage{sidecap}

%\usepackage[font=footnotesize]{caption}
%\usepackage{caption}
%\usepackage[font=footnotesize, figurename=Figure, labelsep=endash]{caption}
%\usepackage{multirow}

\setlength\parindent{0pt}

\begin{document}
%\input{prior_results_and_BI_rudnick}

{\bf \Large Project Summary}


{\bf Intellectual Merit:} 
%How important is the proposed activity to advancing knowledge and understanding within its own field or across different fields? 
%How well qualified is the proposer (individual or team) to conduct the project? (If appropriate, the reviewer will comment on the quality of the prior work.) 
%To what extent does the proposed activity suggest and explore creative, original, or potentially transformative concepts? How well conceived and organized is the proposed activity? 
%Is there sufficient access to resources?


{\bf Broader Impact:} 

This proposal resonates with the National Science Foundation's {broader impacts}
criteria on many levels.  
First, the proposal helps promotes teaching and learning by
promoting
modeling approach to teaching HS physics, integrating problem-based learning into general physics,
and the introduction an astronomy 
concentrations within the physics major to increase the number of majors.
Nationally, astronomy traditionally draws a higher fraction of women than physics, so 
the introduction of the astronomy concentration should attract more female students, 
a group that is significantly under-represented in phyiscs.
Second, the project provides hands-on training and learning for tens of 
undergraduate students through research.  
The Siena undergraduate students will be 
encouraged to become involved in all aspects
of research, including data aquisition at world-class observatories, on-campus 
data reduction and analysis, and presentation of results at national
conferences and through publication in peer-reviewed journals.
The computer analysis, data interpretation, and presentation skills the
undergraduates learn 
will be essential for success in
the workplace, the classroom, or graduate education in any field of science. 
Finally,
the proposal enhances the infrastructure for research and education at Siena College 
by formalizing collaborations
with the ALFALFA team, several of whom are located in New York State and already serve as an
extended network of mentors for Siena undergraduates.
The proposal will also enable Siena to conduct remote observing sessions at Arecibo.

The scientific results of will be disseminated broadly through publication in peer-reviewed journals,
online database, presentation at regional, national and international meetings.  
I will provide a full catalog for the scientific community that will include
an extensive array of primary and derived data products.
This will be a much-needed reference for galaxy evolution modelers,
particularly those who model the evolution of galaxies. 
The pedagogic results will also be disseminated broadly through 
publication in peer-reviewed journals and presentations at regional and national conferences.  
Of particular interest is the impact that problem-based learning has
on student retention and research readiness.  
In addition, we will develop a new assessment tool that measures a student's
ability to think independently and solve real-world problems.  This
will be of wide interest to institutions looking to implement
similar research-focused curricular changes.


\end{document}